---
title: "p8105_hw1_wl2926"
author: "Wenwen Li"
date: 2023-09-21
output: github_document
---


# Problem 1

```{r setup, include = FALSE}
# install and load package
library(tidyverse)
# install.packages("moderndive")
library(moderndive)
# load datasets
data("early_january_weather")
```

## Decribe the Dataset

Write a short description of the dataset using inline R code:
* the variables in this dataset, including names / values of important variables
* the size of the dataset (using nrow and ncol)
* the mean temperature

### Size of the dataset
use nrow and ncol function
```{r}
nrow(early_january_weather)
ncol(early_january_weather)
```
The dataset contains 358 observationss and 15 variables

### Variables
Getting list of variable names
```{r}
colnames(early_january_weather)
```
Important variables may include:
time_hour: Time of the measurement.
temp: Temperature.
humid: Humidity.

##use 'skimr::skim' function to look at the data for the first setp
```{r}
skimr::skim(early_january_weather)
```
There are 1 character variable, 13 numeric variables and 1 POSIXct variable.

### the mean temperature
Using functions to get the mean temperature
```{r}
mean(early_january_weather$temp, na.rm=TRUE)
```
The mean of the temperature is 39.58212.

## Make a scatterplot of temp(y) vs time_hour(x)
```{r}
set.seed(1)
scatter_plot<-ggplot(early_january_weather,aes(x=time_hour,y=temp,color=humid))+geom_point()
print(scatter_plot)
```
## Export Scatterplot
```{r}
ggsave("sctter_plot.pdf", plot = scatter_plot,height = 4, width = 6)
```


# Problem 2

Create a data frame comprised of:

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

## Create data frame
```{r}
set.seed(1)
rnorm_sample = rnorm(10, sd = 1)
print(rnorm_sample)
```

##  a logical vector indicating whether elements of the sample are greater than 0
```{r}
set.seed(1)
vec_logical <- rnorm_sample > 0
print(vec_logical)
```

## a character vector of length 10
```{r}
vec_char = c("uni", "cute", "westie", "puppy", "girl","white","little","small","dog","really")
print(vec_char)
```

## a factor vector of length 10, with 3 different factor “levels”
```{r}
vec_factor = factor(vec_char, levels = c("uni", "cute", "westie"))
print(vec_factor)
```
## Create the dataframe
```{r}
df <- data.frame(
  rnorm_sample = rnorm_sample,
  vec_logical = vec_logical,
  vec_char = vec_char,
  vec_factor = vec_factor
)
```
## Calculate the mean of each variable using pull from the dataframe
```{r}
mean(rnorm_sample)
mean(vec_logical)
mean(vec_char)
mean(vec_factor)
```
### Load necessary libraries
```{r}
library(tidyverse)
mean_rnorm_sample <- mean(pull(df, rnorm_sample))
mean_vec_logical <- mean(pull(df, vec_logical))
mean_vec_char <- mean(pull(df, vec_char))
mean_vec_factor <- mean(pull(df, vec_factor))
```
It only works for numeric or bool variables; some variable cannot be calculated.

## applies the as.numeric function
```{r}
mean_rnorm_sample <- mean(pull(df, rnorm_sample))
mean_vec_logical <- mean(as.numeric(pull(df, vec_logical)))
mean_vec_char <- mean(as.numeric(pull(df, vec_char)))
mean_vec_factor <- mean(as.numeric(pull(df, vec_factor)))

# Print the means
print("Mean of rnorm_sample:")
print(mean_rnorm_sample)

print("Mean of vec_logical:")
print(mean_vec_logical)

print("Mean of vec_char:")
print(mean_vec_char)

print("Mean of vec_factor:")
print(mean_vec_factor)
```
For the logical vector (vec_logical), as.numeric will convert TRUE to 1 and FALSE to 0.For the character vector (vec_char), as.numeric will attempt to convert characters to numeric values. If it can't make a meaningful conversion (most cases), it will result in NA (Not Available) for those elements.For the factor vector (vec_factor), as.numeric will convert the underlying numerical representation of the factor levels. Each factor level is internally represented by integers.
