---
title: "p8105_hw1_wl2926"
author: "Wenwen Li"
date: 2023-09-21
output: github_document
---


# Problem 1

```{r setup, include = FALSE}
# install and load package
# install.packages("moderndive")
library(moderndive)
# load datasets
data("early_january_weather")
```

## Decribe the Dataset

Write a short description of the dataset using inline R code:
* the variables in this dataset, including names / values of important variables
* the size of the dataset (using nrow and ncol)
* the mean temperature

### Size of the dataset
use nrow and ncol function
```{r}
nrow(early_january_weather)
ncol(early_january_weather)
```
The dataset contains 358 observationss and 15 variables

### Variables
Getting list of variable names
```{r}
colnames(early_january_weather)
```
use 'skimr::skim' function to look at the data for the first setp
```{r}
skimr::skim(early_january_weather)
```
There are 1 character variable, 13 numeric variables and 1 POSIXct variable.

### the mean temperature
Using functions to get the mean temperature
```{r}
mean(early_january_weather$temp, na.rm=TRUE)
```
The mean of the temperature is 39.58212.

### Make a scatterplot of temp(y) vs time_hour(x)
```{r}
scatter_plot <- ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  labs(x = "Time Hour", y = "Temperature", color = "Humidity") +
  theme_minimal()
```

#


Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.